---
title: "SQMB 2022/23 – Summative Assessment 2"
author: "PUT YOUR EXAM NUMBER HERE"
date: "`r Sys.Date()`"
output: 
  pdf_document: 
    number_sections: yes
    latex_engine: xelatex
    keep_tex: yes
    toc: true
mainfont: Arial
---
\newpage

```{r setup, include=FALSE}
# PLEASE DON'T CHANGE THESE SETTINGS
knitr::opts_chunk$set(echo = FALSE)  # This line hides all code in the output
knitr::opts_knit$set(root.dir = here::here())

library(tidyverse)
library(brms)
library(broom.mixed)
library(posterior)
library(knitr)
```


# Set-up instructions

- **Before changing anything in this document, render it to PDF** to make sure that everything is rendered as it should be.
  - If you receive the error `Error in library (knitr) : there is no package called 'knitr'`, then in the console, run `install.packages('knitr')` and try again.
- Include your **exam number as the author** in the document preamble. 
- Before you submit, delete the "Set-up instructions" and "Table and figure examples" sections. **Your submission should contain only your own work.**


Instructions for completing the assessment itself are given in `sqmb-s2/README.md`.


# Table and figure examples

## How to present a data frame as a table with a caption

The first step is to create a data frame that contains only the information you want to display in the table.
(Some helpful functions for modifying a data frame include tidyverse's `filter()` and `select()`.)

I'll illustrate this using R's built-in data frame `iris`.
This data frame contains information about the shape and size of 150 different iris flowers, 50 each from three different species.
Here, I'll create a table displaying only the first six rows of this data frame.

```{r setup-data-example}
# Create the data frame that you'll display (I'm using head() to get the first six rows of iris).
brief_iris <- head(iris)
```

Once your data frame is ready, it can be displayed using the function `kable()` from the library `knitr`.
`kable()` takes in a data frame and converts it into a markdown table.
Then, when the document is knit to PDF, this markdown table is rendered into a professional-looking table.

`kable()` also has an argument `caption`.
Use this argument to give the table a caption that describes for the reader what the table is showing.

```{r table-example}
# Use kable() to create the markdown table, and use the `caption` argument to add a caption to the table.
kable(
  brief_iris,
  caption = 'Sepal and petal measurements in centimetres for six setosa irises.'
)
```


## How to present a ggplot as a figure with a caption

For illustration, I'll create a scatter plot that shows the association between the irises' petal width and petal length, with points coloured by species.

Including a caption for a figure works a little differently than for a table: you have to include the text caption in the header of the code chunk.
You can do this using the chunk option `fig.cap`.
Have a look at the example in the code.

```{r figure-example, fig.cap = 'Petal length in irises is positively associated with petal width. Setosas have the smallest petals, while those of versicolors and virginicas are larger.'}

# Create the plot that will be shown along with the caption in the chunk's `fig.cap` option.
iris %>% 
  ggplot(aes(x = Petal.Length, y = Petal.Width, colour = Species)) +
  labs(x = 'Petal length (cm)',
       y = 'Petal width (cm)') +
  geom_point()
```

More information about including tables and figures in your Rmarkdown document can be found here: <https://rmd4sci.njtierney.com/figures-tables-captions-.html>.

(Don't worry if the tables or figures appear in a different place in the PDF than they do in the Rmd file.
Tables and figures might "float" around a little, based on what the typesetting algorithm thinks looks best, and this is to be expected.)
